Supplementary Information

### 2020-09-01 doc/manuscript/MEE_manuscript.Rmd
moved nocite section

---
title: ''
output: word_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Table 1 | Sites included in this analysis**. Here and throughout, sites are ordered by latitude. Additional site information is provided in Table S1, and species and their sample sizes are detailed in Tables S2-S3. *Climate will be filled in based on CRU data.*
![ ](tables_figures/sites_table.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite metadata field at the top of the document
```

>>>>

---
title: ''
output: word_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Table 1 | Sites included in this analysis**. Here and throughout, sites are ordered by latitude. Additional site information is provided in Table S1, and species and their sample sizes are detailed in Tables S2-S3. *Climate will be filled in based on CRU data.*
![ ](tables_figures/sites_table.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019; @aus_de_ar_tree_2018; @bumann_assessing_2019
---
